%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%% Kimin Yun's LaTeX Template %%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't like 10pt? Try 11pt or 12pt
\documentclass[10pt]{article}

% This is a helpful package that puts math inside length specifications
\usepackage{calc}
\usepackage{kotex}

% Simpler bibsection for CV sections
% (thanks to natbib for inspiration)
\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{1em}
\newlength{\bibsep}
 {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newenvironment{bibsection}%
        {\vspace{-\baselineskip}\begin{list}{}{%
       \setlength{\leftmargin}{\bibhang}%
       \setlength{\itemindent}{-\leftmargin}%
       \setlength{\itemsep}{\bibsep}%
       \setlength{\parsep}{\z@}%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}
\makeatother

% Layout: Puts the section titles on left side of page
\reversemarginpar

%
%         PAPER SIZE, PAGE NUMBER, AND DOCUMENT LAYOUT NOTES:
%
% The next \usepackage line changes the layout for CV style section
% headings as marginal notes. It also sets up the paper size as either
% letter or A4. By default, letter was used. If A4 paper is desired,
% comment out the letterpaper lines and uncomment the a4paper lines.
%
% As you can see, the margin widths and section title widths can be
% easily adjusted.
%
% ALSO: Notice that the includefoot option can be commented OUT in order
% to put the PAGE NUMBER *IN* the bottom margin. This will make the
% effective text area larger.
%
% IF YOU WISH TO REMOVE THE ``of LASTPAGE'' next to each page number,
% see the note about the +LP and -LP lines below. Comment out the +LP
% and uncomment the -LP.
%
% IF YOU WISH TO REMOVE PAGE NUMBERS, be sure that the includefoot line
% is uncommented and ALSO uncomment the \pagestyle{empty} a few lines
% below.
%

%% Use these lines for letter-sized paper
\usepackage[paper=letterpaper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=1.2in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=1in,               % 1 inch margins
            includemp]{geometry}

%% Use these lines for A4-sized paper
%\usepackage[paper=a4paper,
%            %includefoot, % Uncomment to put page number above margin
%            marginparwidth=30.5mm,    % Length of section titles
%            marginparsep=1.5mm,       % Space between titles and text
%            margin=25mm,              % 25mm margins
%            includemp]{geometry}

%% More layout: Get rid of indenting throughout entire document
\setlength{\parindent}{0in}

%% This gives us fun enumeration environments. compactitem will be nice.
\usepackage{paralist}

%% Reference the last page in the page number
%
% NOTE: comment the +LP line and uncomment the -LP line to have page
%       numbers without the ``of ##'' last page reference)
%
% NOTE: uncomment the \pagestyle{empty} line to get rid of all page
%       numbers (make sure includefoot is commented out above)
%
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
%\pagestyle{empty}      % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                    \arabic{page} of \protect\pageref*{LastPage} % +LP
%                    \arabic{page}                               % -LP
                    \hfill \,}}

% Finally, give us PDF bookmarks
\usepackage{xcolor,hyperref}
% --- refined palette ---
\definecolor{accent}{HTML}{2F4A6B}     % deep slate-blue (section titles, name)
\definecolor{rulecol}{HTML}{C9D2DE}    % light rule between sections
\definecolor{subtle}{HTML}{5B6470}     % muted text (subtitle)
\hypersetup{colorlinks,breaklinks,
            linkcolor=accent,urlcolor=accent,
            anchorcolor=accent,citecolor=accent}

%%%%%%%%%%%%%%%%%%%%%%%% End Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%% Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The title (name) with a horizontal rule under it
%
% Usage: \makeheading{name}
%
% Place at top of document. It should be the first thing.
\newcommand{\makeheading}[2]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
                {\Huge \bfseries \color{accent} #1}\\[0.18\baselineskip]%
                {\normalsize \color{subtle} #2}\\[0.30\baselineskip]%
                 {\color{accent}\rule{\columnwidth}{1.3pt}}%
         \end{minipage}\vspace{0.2\baselineskip}}

% The section headings
%
% Usage: \section{section name}
%
% Follow this section IMMEDIATELY with the first line of the section
% text. Do not put whitespace in between. That is, do this:
%
%       \section{My Information}
%       Here is my information.
%
% and NOT this:
%
%       \section{My Information}
%
%       Here is my information.
%
% Otherwise the top of the section header will not line up with the top
% of the section. Of course, using a single comment character (%) on
% empty lines allows for the function of the first example with the
% readability of the second example.
\renewcommand{\section}[2]%
        {\pagebreak[2]\vspace{1.15\baselineskip}%
         \phantomsection\addcontentsline{toc}{section}{#1}%
         {\color{rulecol}\rule{\columnwidth}{0.5pt}}\par\vspace{0.40\baselineskip}%
         \hspace{0in}%
         \marginpar{\vspace{0.5pt}%
         \raggedright \sffamily\bfseries\footnotesize \color{accent} #1}#2}

% An itemize-style list with lots of space between items
\newenvironment{outerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1]}{\end{itemize}%
         \vspace{-.6\baselineskip}}

% An environment IDENTICAL to outerlist that has better pre-list spacing
% when used as the first thing in a \section
\newenvironment{lonelist}[1][\enskip\textbullet]%
        {\vspace{-\baselineskip}\begin{list}{#1}{%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}

% An itemize-style list with little space between items
\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{compactitem}[#1]}{\end{compactitem}}

% An environment IDENTICAL to innerlist that has better pre-list spacing
% when used as the first thing in a \section
\newenvironment{loneinnerlist}[1][\enskip\textbullet]%
        {\vspace{-\baselineskip}\begin{compactitem}[#1]}
        {\end{compactitem}\vspace{-.6\baselineskip}}

% To add some paragraph space between lines.
% This also tells LaTeX to preferably break a page on one of these gaps
% if there is a needed pagebreak nearby.
\newcommand{\blankline}{\quad\pagebreak[2]}

% Uses hyperref to link DOI
\newcommand\doilink[1]{\href{http://dx.doi.org/#1}{#1}}
\newcommand\doi[1]{doi:\doilink{#1}}


%%%%%%%%%%%%%%%%%%%%%%%% End Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\makeheading{윤기민 \textnormal{\large Kimin Yun}}{책임연구원, 한국전자통신연구원(ETRI) \quad·\quad 부교수, 과학기술연합대학원대학교(UST)\\[2pt]Principal Researcher, ETRI \quad·\quad Associate Professor, UST}

\section{연락처 (Contact Information)}
%
% NOTE: Mind where the & separators and \\ breaks are in the following
%       table.
%
% ALSO: \rcollength is the width of the right column of the table
%       (adjust it to your liking; default is 1.85in).
%
\newlength{\rcollength}\setlength{\rcollength}{1.0in}%
%
\begin{tabular}[t]{@{}p{\textwidth-\rcollength}p{\rcollength}}
한국전자통신연구원 (ETRI) 인공지능창의연구소 시각지능연구실 \\
과학기술연합대학원대학교 (UST) 인공지능전공 ETRI 스쿨 \\
대전광역시 유성구 가정로 218 (34129) \\
218 Gajeong-ro, Yuseong-gu, Daejeon, 34129, South Korea \\
\\
\textit{Webpage:} \href{https://kimin-yun.github.io}{https://kimin-yun.github.io} \\
\textit{Google Scholar:} \href{https://scholar.google.co.kr/citations?user=fcVfLCkAAAAJ&hl=ko&citsig=AMstHGQjrQzMFrSSjkfQPG-JmXoXR8HNwQ}{Link} \\
\textit{E-mail:} {kimin.yun@etri.re.kr} \\
\end{tabular}


%\section{Objective}
%%
%Placement in a postdoctoral researcher in

\section{국적 (Citizenship)}
%
대한민국 (Republic of Korea)


\section{연구 관심사 (Research Interests)}
%
컴퓨터 비전, 멀티모달 인공지능 모델, 실세계 AI 응용 \\
Computer Vision, Multimodal AI Model, Real-world AI Application 

\section{경력 (Career)}
\href{https://etri.re.kr/eng/main/main.etri}{한국전자통신연구원 (Electronics and Telecommunications Research Institute, ETRI)}
\begin{outerlist}
\item[] 책임연구원 (Principal Researcher), 2026.3--현재
\item[] 선임연구원 (Senior Researcher), 2019.3--2026.3
\item[] 연구원 (Researcher), 2017.2--2019.3
\end{outerlist}
\vspace{0.5cm}
\href{https://www.ust.ac.kr/eng/}{과학기술연합대학원대학교 (University of Science and Technology, UST)} 
\begin{outerlist}
\item[] 부교수 (Associate Professor), 2025.3--현재
\end{outerlist}



\section{학력 (Education)}
%
\href{http://www.useoul.edu/}{\textbf{서울대학교 (Seoul National University)}}, Seoul, Korea
\begin{outerlist}

\item[] 박사 (Ph.D.),
        \href{http://ece.snu.ac.kr/en}
             {전기·정보공학부 (Department of Electrical and Computer Engineering)}, 2017.2
        \begin{innerlist}
        		\item Thesis Title: \emph{Background-Centric Approach for Moving Object Detection in Moving Cameras}
        		\item Adviser: {Prof. Jin Young Choi}
        		\item Area of Study: Machine Learning and its application to computer vision area
        \end{innerlist}

\item[] 학사 (B.S.),
        \href{http://ece.snu.ac.kr/en}
             {전기공학부 (Department of Electrical Engineering)}, 2010.2
        \begin{innerlist}
            \item Thesis Title: \emph{Video Stabilization System for Real-time Video Surveillance System}
            \item Graduated Cum Laude
        \end{innerlist}

\end{outerlist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{학술지 논문 (Journal Publications)} \begin{bibsection}

% \item Hyung-Il Kim, \textbf{Kimin Yun}, Kangmin Bae, and Jinyoung Moon, 
% 				``Background memory-assisted zero-shot video object segmentation for unmanned aerial and ground vehicles",
% 				\emph{ETRI Journal}, 2023.  

\item \textbf{Kimin Yun}$\dagger$, and Yuseok Bae, 
				``Zero-Shot Anomaly Segmentation via Query-Level Uncertainty Analysis",
				\emph{IEEE Access (SCIE)}, 2026. ($\dagger$ Corresponding author)

\item Yu-Hyun Shin*, \textbf{Kimin Yun*,$\dagger$}, and Yuseok Bae, 
				``Fast Adversarial Robustness Recovery against Model Parameter Exposure through Hopfield-type Neural ODEs",
				\emph{ETRI Journal (SCIE)}, 2026 (accepted). (* Equal contribution, $\dagger$ Corresponding author)

\item Sunoh Kim, \textbf{Kimin Yun}, and Daeho Um, 
				``Finding Optimal Video Moment without Training: Gaussian Boundary Optimization for Weakly Supervised Video Grounding",
				\emph{IEEE Transactions on Multimedia (SCIE)}, 2026.

\item Jeonghyo Song, \textbf{Kimin Yun}, Dae Ung Jo, Jinyoung Kim, and Youngjoon Yoo, 
				``Multi-Agent Visual Reasoning for Out-of-Distribution Detection in Complex Road Environments",
				\emph{IEEE Access (SCIE)}, 2025.

\item \textbf{Kimin Yun}, Hyung-Il Kim, Kangmin Bae, and Jinyoung Moon, 
				``Background memory-assisted zero-shot video object segmentation for unmanned aerial and ground vehicles",
				\emph{ETRI Journal (SCIE)}, 2023.  

\item Hyung-Il Kim, \textbf{Kimin Yun}, and Yong Man Ro, 
				``Face Shape-Guided Deep Feature Alignment for Face Recognition Robust to Face Misalignment",
				\emph{IEEE Transactions on Biometrics, Behavior, and Identity Science}, 2022.  

\item Geonu Lee, \textbf{Kimin Yun}, and Jungchan Cho, 
				``Occluded Pedestrian-Attribute Recognition for Video Sensors Using Group Sparsity",
				\emph{Sensors (SCIE)}, 2022.     

\item Hyundong Jin, \textbf{Kimin Yun}, and Eunwoo Kim, 
				``Gating Mechanism in Deep Neural Networks for Resource-Efficient Continual Learning",
				\emph{IEEE Access (SCIE)}, 2022. 

    \item \textbf{Kimin Yun}, and Jongwon Choi, 
				``Adaptive Network Compression using Block Removal and Recycling Mechanisms",
				\emph{Techart: Journal of Arts and Imaging Science}, 2021.  


\item Youngwan Lee, Hyung-Il Kim, \textbf{Kimin Yun}, and Jinyoung Moon, 
				``Diverse Temporal Aggregation and Depthwise Spatiotemporal Factorization for Efficient Video Classification",
				\emph{IEEE Access (SCIE)}, 2021.  

	    \item Geonu Lee, \textbf{Kimin Yun}, and Jungchan Cho, 
				``Improved Human-Object Interaction Detection through On-the-Fly Stacked Generalization",
				\emph{IEEE Access (SCIE)}, 2021.  

		\item \textbf{Kimin Yun}, Jongyoul Park, and Jungchan Cho, 
				``Robust Human Pose Estimation for Rotation via Self-Supervised Learning",
				\emph{IEEE Access (SCIE)}, 2020.  

		\item \textbf{Kimin Yun}, Yongjin Kwon, Sungchan Oh, Jinyoung Moon, and Jongyoul Park,
				``Vision-based Garbage Dumping Action Detection for Real-World Surveillance Platform",
				\emph{ETRI Journal (SCIE)}, 2019. (Best Paper Award)

		\item  Sangdoo Yun, Jongwon Choi, Youngjoon Yoo, \textbf{Kimin Yun}, and Jin Young Choi
				``Action-Driven Visual Object Tracking with Deep Reinforcement Learning",
				\emph{IEEE Transactions on Neural Networks and Learning Systems (TNNLS) (SCIE)}, 2018.  


		\item \textbf{Kimin Yun}, Jongin Lim, and Jin Young Choi,
				``Scene Conditional Background Update for Moving Object Detection in a Moving Camera",
				\emph{Pattern Recognition Letters (SCIE)}, 2017.  


		\item  \textbf{Kimin Yun}, YoungJoon Yoo, and Jin Young Choi,
				``Motion Interaction Field for Detection of Abnormal Interactions",
				\emph{Machine Vision and Applications (SCIE)}, 2017.


		\item Soo Wan Kim, Shimin Yin, \textbf{Kimin Yun}, and Jin Young Choi,
				``Spatio-temporal weighting in local patches for direct estimation of camera motion in video stabilization",
				\emph{Computer Vision and Image Understanding (SCIE)}, Vol.118, pp.71-83, Jan 2014.

		\item Soo Wan Kim, \textbf{Kimin Yun}, Kwang Moo Yi, Sun Jung Kim and Jin Young Choi,
				``Detection of moving objects with a moving camera using non-panoramic background model",
				\emph{Machine Vision and Applications (SCIE)}, pages 1015-1028, Vol.24, Issue 5, July 2013.


\end{bibsection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{국제 학회 논문 (International Conference Publications)} \begin{bibsection}
        \item Yujeong Oh, Taehoon Kim, Mingyu Lee, \textbf{Kimin Yun}$\dagger$, and Jongwon Choi$\dagger$, 
					``Dynamic Augmentation Strategy Selection for Incremental Object Detection",
					 \emph{International Conference on Pattern Recognition (\textbf{ICPR})}, 2026. ($\dagger$ Co-corresponding authors)

        \item Minjae Bang*, Juhyeon Han*, Yuseok Bae, Sunok Kim$\dagger$, and \textbf{Kimin Yun}$\dagger$, 
					``Reasoning-augmented Vision-Language Models for Improved Competency in Scene Text Recognition",
					 \emph{International Conference on Consumer Electronics (\textbf{ICCE}) Asia}, 2025. (* Equal contribution, $\dagger$ Corresponding author)

        \item \textbf{Kimin Yun}, Kangmin Bae, and Yuseok Bae, 
				``Task-Adaptive Open-Set Detection with Prompt-Tuned Adaptors",
				 \emph{IEEE International Conference on Advanced Visual and Signal-Based Systems (\textbf{AVSS})}, 2025.


        \item Jeonghyo Song, \textbf{Kimin Yun}, DaeUng Jo, Jinyoung Kim, and Youngjoon Yoo, 
				``CoT-Segmenter: Enhancing OOD Detection in Dense Road Scenes via Chain-of-Thought Reasoning",
				  \emph{IEEE International Conference on Advanced Visual and Signal-Based Systems (\textbf{AVSS})}, 2025.


        \item JinYoung Kim, DaeUng Jo, \textbf{Kimin Yun}, Jeonghyo Song, Youngjoon Yoo
				``Distributional Uncertainty for Out-of-Distribution Detection",
				  \emph{IEEE International Conference on Advanced Visual and Signal-Based Systems (\textbf{AVSS})}, 2025.


        \item Hyung-Il Kim*, \textbf{Kimin Yun*}, Jun-Seok Yun, and Yuseok Bae, 
        ``Task-Specific Adaptation of Segmentation Foundation Model via Prompt Learning", 
        \emph{European Conference on Computer Vision Workshop on Out Of Distribution Generalization in Computer Vision (\textbf{ECCVW})}, 2024.
        * equal contribution

        \item \textbf{Kimin Yun}*, Jeonghoon Song*, and Yuseok Bae, 
        ``Training-Free OOD Object Detection Leveraging Pre-trained Segmentation Model Competency", 
        \emph{ The 15th International Conference on ICT Convergence (ICTC)}, 2024.
        * equal contribution

        \item Sunoh Kim, Taegil Ha, \textbf{Kimin Yun}, and Jin Young Choi, 
				``SWAG-Net: Semantic Word-Aware Graph Network for Temporal Video Grounding",
				 \emph{ACM International Conference on Information and Knowledge Management (\textbf{CIKM})}, 2022.

     	\item Youngwan Lee, Joong-Won Hwang, Hyung-Il Kim, \textbf{Kimin Yun}, Yongjin Kwon, Yuseok Bae, and Sung Ju Hwang, 
				``Localization Uncertainty Estimation for Anchor-Free Object Detection",
				 \emph{European Conference on Computer Vision Workoshop on Uncertainty Quantification for Computer Vision (\textbf{ECCVW})}, 2022.


	\item Kangmin Bae*, \textbf{Kimin Yun*}, Jungchan Cho, and Yuseok Bae
				``The Dataset and Baseline Models to Detect Human Postural States Robustly against Irregular Postures",
				 \emph{IEEE Int'l Conf on Advanced Video and Signal-based Surveillance (\textbf{AVSS})}, 2021.
				 * equal contribution
				 
	\item Sunoh Kim, \textbf{Kimin Yun}, and Jin Young Choi, 
				``Position-aware Location Regression Network for Temporal Video Grounding",
				 \emph{IEEE Int'l Conf on Advanced Video and Signal-based Surveillance (\textbf{AVSS})}, 2021.

	\item \textbf{Kimin Yun}, Hyungil Kim, Kangmin Bae, and Jongyoul Park
				``Unsupervised Moving Object Detection through Background Models for PTZ Camera",
				 \emph{International Conference on Pattern Recognition (\textbf{ICPR})}, 2020.
				 
	 \item Kangmin Bae*, \textbf{Kimin Yun*}, Hyungil Kim, Youngwan Lee, and Jongyoul Park
				``Anti-Litter Surveillance based on Person Understanding via Multi-task Learning",
				 \emph{British Machine Vision Conference (\textbf{BMVC})}, 2020. 
				 * equal contribution
				 
	 \item Sunoh Kim, \textbf{Kimin Yun}, Jongyoul Park, and Jin Young Choi
				``Skeleton-based Action Recognition of People Handling Objects",
				 \emph{IEEE Winter Conference on Applications of Computer Vision (\textbf{WACV})}, 2019. 
	\item Jeong-Min Seo, Haanju Yoo, \textbf{Kimin Yun}, Hyunil Kim, and Sang-Il Choi
				``Behavior Recognition of a Person in a Daily Video Using Joint Position Information",
				 \emph{IEEE International Conference on Artificial Intelligence and Knowledge Engineering Workshop on AI Bigdata Cloud Technologies}, 2018. 			 
	\item  Sangdoo Yun, Jongwon Choi, Youngjoon Yoo, \textbf{Kimin Yun}, and Jin Young Choi,
				``Action-Decision Network for Visual Tracking with Deep Reinforcement Learning",
				 \emph{IEEE International Conference on Computer Vision and Pattern Recognition (\textbf{CVPR})}, 2017.
	\item Byeongho Heo, \textbf{Kimin Yun} and Jin Young Choi,
				``Appearance and Motion based Deep Learning Architecture for Moving Object Detection in Moving Camera",
				 \emph{IEEE International Conference on Image Processing (\textbf{ICIP})}, 2017. 
		\item  \textbf{Kimin Yun}, Jongin Lim, Sangdoo Yun, Soo Wan Kim, and Jin Young Choi,
				``Attention-Inspired Moving Object Detection in Monocular Dashcam Videos",
				 \emph{23rd International Conference on Pattern Recognition (\textbf{ICPR})}, 2016.
		\item  Sangdoo Yun, \textbf{Kimin Yun}, Jongwon Choi, and Jin Young Choi,
				``Density-Aware Pedestrian Proposal Networks for Robust People Detection in Crowded Scenes",
				 \emph{International Workshop on Crowd Understanding in conjuction with ECCV (\textbf{ECCVW})}, 2016.
		\item YoungJoon Yoo, \textbf{Kimin Yun}, Sangdoo Yun, JongHee Hong, Hawook Jeong, and Jin Young Choi,
				``Visual Path Prediction in Complex Scenes with Crowded Moving Objects",
				 \emph{IEEE Conference on Computer Vision and Pattern Recognition (\textbf{CVPR})}, 2016.
		\item \textbf{Kimin Yun} and Jin Young Choi,
				``Robust and Fast Moving Object Detection in a Non-Stationary Camera via Foreground Probability based Sampling",
				 \emph{IEEE International Conference on Image Processing (\textbf{ICIP})}, 2015.
		\item ByeongJu Lee, Jongwon Choi, \textbf{Kimin Yun}, and Jin Young Choi,
				``Gradient Preserving RGB-to-Gray Conversion using Random Forest",
				 \emph{IEEE International Conference on Image Processing (\textbf{ICIP})}, 2015.
		\item ByeongJu Lee, \textbf{Kimin Yun}, Jongwon Choi, and Jin Young Choi,
				``Robust Pan-Tilt-Zoom Tracking via Optimization Combining Motion Features and Appearance Correlations "`,
				 \emph{IEEE International Conf. on Advanced Video and Signal based Surveillance (\textbf{AVSS})}, 2015.  
		\item \textbf{Kimin Yun}, Jiyun Kim, Soo Wan Kim, Hawook Jeong, and Jin Young Choi,
				``Learning with Adaptive Rate for Online Detection of Unusual Appearance",
				\emph{10th International Symposium on Visual Computing (\textbf{ISVC})}, 2014.
		\item  Tushar Sandhan, \textbf{Kimin Yun}, and Jin Young Choi,
				``Proximity Clustering for Revealing a Semantically Dominant Class",
				\emph{10th International Symposium on Visual Computing (\textbf{ISVC})}, 2014.
		\item \textbf{Kimin Yun}, Hawook Jeong, Kwang Moo Yi, Soo Wan Kim, and Jin Young Choi,
				``Motion Interaction Field for Accident Detection in Traffic Surveillance Video",
				\emph{22nd International Conference on Pattern Recognition (\textbf{ICPR})}, 2014.
        \item  Sangdoo Yun, \textbf{Kimin Yun}, Soo Wan Kim, Youngjoon Yoo and Jiyeoup Jeong.
              ``Visual Surveillance Briefing System: Event-based Video Retrieval and Summarization",
              \emph{IEEE International Conf. on Advanced Video and Signal based Surveillance (\textbf{AVSS})}, 2014.
		\item Kwang Moo Yi, \textbf{Kimin Yun}, Soo Wan Kim, Hyung Jin Chang, Hawook Jeong, and Jin Young Choi,
				``Detection of Moving Objects with Non-Stationary Cameras in 5.8ms: Bringing Motion Detection to your Mobile Device",
				\emph{IEEE Int. workshop on Mobile vision, in conjunction with CVPR  (\textbf{CVPRW})}, 2013. (Best Paper Award)
		\item \textbf{Kimin Yun}, Soo Wan Kim, and Jin Young Choi,
				``Probabilistic Approach with Three Hierarchies of Motion Estimation for Video Stabilization",
				\emph{IEEE Digital Image Computing: Techniques and Applications (\textbf{DICTA})}, 2011.
				



\end{bibsection}


\section{국내 학회 논문 (Domestic Conference Publications)} \begin{bibsection}

        \item 김소정, 배유석, \textbf{윤기민}, ``한국어 장면 텍스트 인식에서 VLM의 시각적 역량 및 강건성 분석", \emph{지능정보 및 제어 학술대회}, 2026.

        \item 한주현, 방민재, 배유석, \textbf{윤기민}, ``VLM의 한국어 장면 텍스트 이해를 위한 학습 데이터 구성과 CoT 추론 효과 분석", \emph{인공지능신호처리 학술대회}, 2025.

        \item 송정훈, \textbf{윤기민}, 배유석, "Anomalous Object Detection in Road Scenes based on  Out-of-Distribution object Characteristics", 인공지능 신호처리 학술대회, 2024
        
        \item 조재호, 배유석, 천용석, \textbf{윤기민}, "Fine-tuning Open-Set Detectors through Self-Supervised Learning and Data Selection Strategies: A Case Study in Banner Detection", 한국컴퓨터 종합 학술대회, 2024
        
        \item	부원국, 배강민, \textbf{윤기민}, 배유석, "Development of Real-world Fallen Person Detection using Multi-task Learning", 대한전자공학회 학술 대회 (하계), 2023
        
        \item	송길재, 김진아, 배강민, \textbf{윤기민}, 배유석, "A Framework for Effective Multi-camera Batch Inference and Event Alert", 한국컴퓨터 종합 학술대회, 2022
        
        \item	김진아, 송길재, 배강민, \textbf{윤기민}, 배유석, "Improvements on Real-world Domain and Person Understanding via Optimal Combination of Training Dataset and Model", 한국컴퓨터 종합 학술대회, 2022

		\item \textbf{윤기민}, 박종열, "동적 카메라 동적 물체 탐지를 위한 세밀 배경 학습법",   \emph{제27회 영상처리 및 이해에 관한 워크샵 (\textbf{IPIU})},  2019.
  
		\item 서정민, 유한주, 최상일, \textbf{윤기민}, "행동 이해용 학습데이터 생성을 위한 어노테이션 도구 개발", 2018년도 한국통신학회 하계종합학술대회, 2018.
  
		\item 허병호, \textbf{윤기민}, 정지엽, 최진영, "외형 및 움직임 정보를 활용한 딥 러닝 기반의 동적 카메라 동적 물체 탐지 기술 ", \emph{제27회 영상처리 및 이해에 관한 워크샵 (\textbf{IPIU})}, 2017.
  
		\item 정지엽, 최종원, 이병주, \textbf{윤기민}, 최진영,
				``가우시안 프로세스 회기 함수를 이용한 환경변화에 강인한 군중밀도 감지 알고리즘 개발",
				 \emph{제27회 영상처리 및 이해에 관한 워크샵 (\textbf{IPIU})}, 2015.
		\item \textbf{윤기민}, 윤상두, 최진영,
				``움직임 상호 작용 모델을 통한 군중 폭력 상황 감지",
				 \emph{대한전자공학회 하계종합학술대회}, 2015.
		\item \textbf{윤기민}, 유영준, 김지윤, 최진영,
				``실시간 자동 감시를 위한 비정상 이벤트 검출 통합 플랫폼",
				 \emph{제 15회 전자정보통신 학술대회 (\textbf{CEIC})}, 2013.
		\item \textbf{윤기민}, 김수완, 윤상두, 김지윤, 최진영,
				``감시 영상의 사후 분석을 위한 이벤트 요약 및 분석 애니메이션 기술"`,
				 \emph{대한전자공학회 정기총회 및 추계학술대회}, 2012.
		\item \textbf{윤기민}, 김수완, 최진영,
				``국부움직임의 확률적 정의를 통한 계층적인 영상안정화 기술",
				\emph{제24회 영상처리 및 이해에 관한 워크샵 (\textbf{IPIU})}, 2012.
		\item  김수완, 윤석민, \textbf{윤기민}, 최진영,
				``광역 가중 LKT 방법을 이용한 비디오 안정화 기법",
				\emph{정보 및 제어 학술대회 (\textbf{CICS})}, 2011. 
		\item \textbf{윤기민}, 김수완, 최진영,
				``적분 투영 이미지와 쏠림 현상 지표를 이용한 안정적인 비디오 안정화 기술",
				\emph{대한전자공학회 정기총회 및 추계학술대회}, 2010.
        \item 김수완, \textbf{윤기민}, 이현진, 최진영,
              ``비디오 안정화를 위한 bit-plane 상에서의 강인한 국소 패치 매칭 기법",
              \emph{대한전자공학회 하계종합학술대회}, 2010. 
		


\end{bibsection}






%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{특허 (Patents)} \begin{bibsection}

        \item US Patent US12374094B2, Method and apparatus for feature transforming and processing based on artificial neural network (July, 2025, granted)

        \item US Patent US20250181707A1, System and method for training deep learning networks resistant to adversarial attacks (June, 2025, pending)

        \item US Patent US20250104383A1, Apparatus and method for recognizing image and prompt tuning method related to the same (March, 2025, pending)

        \item US Patent US12142028B2, Object recognition apparatus and method based on environment matching (November, 2024, granted)

       \item US Patent US12056909B2, Method and apparatus for face recognition robust to alignment status of the face (August, 2024, granted)

       \item US Patent US11935296B2, Apparatus and method for online action detection (March, 2024, granted)

        \item US Patent US20230059462A1, Method and apparatus for performing multi-task learning based on task similarity (February, 2023, pending)

        \item US Patent US11527067B2, Electronic device, action instance generation method, and recording medium (December, 2022, granted)

        \item US Patent US11380133B2, Domain adaptation-based object recognition apparatus and method (July, 2022, granted)
    
        \item US Patent 16/834500, Domain adaptation-based object recognition apparatus and method (October, 2020, pending)
        
        \item US Patent US10789470B2, System and method for detecting dynamic object (September, 2020, granted)

        \item US Patent US10311579B2, Apparatus and method for detecting foreground in image (June, 2019, granted)

		\item US Patent 16/541639, Smart glasses and method of selectively tracking target of visual cognition (August, 2019, pending)

		\item US Patent 16/401789, Method and apparatus for detecting a garbage dumping action in real time on video surveillance system (May, 2019, pending)

		\item US Patent 16/033152, SYSTEM AND METHOD FOR DETECTING DYNAMIC OBJECT (July, 2018, pending)

		\item   US Patent US9418320 B2, Apparatus and method for detecting object using PTZ camera (August, 2016, granted)

		\item  KOR Patent 10-2016-0008335 영상에서의 전경 검출 및 방법 (January, 2016, pending)

		\item  KOR Patent 1015134140000 감시 영상 분석 방법 및 시스템 (April, 2015, granted)

		\item  KOR Patent 1014384510000 비고정 카메라 영상에 대한 이중모드 SGM 기반의 이동체 고속 검출 방법 및 이를 위한 컴퓨터로 판독가능한 기록 매체 (September, 2014, granted)

		\item  KOR Patent 1012992370000 팬틸트줌 카메라를 이용한 물체 탐지 장치 및 방법 (August, 2013, granted)





\end{bibsection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{수상 (Awards and Honors)}
2023년 국가연구개발 우수성과 100선 (National R\&D Excellence Top 100, Minister of Science and ICT, South Korea), 참여연구원 \hfill \textbf{2023}
\begin{outerlist}
\item[] \textit{다양한 환경에 적용가능한 영상 이해 인공지능 핵심기술 개발과 시민 안전 분야 실증 및 사업화}%
    \begin{innerlist}
	    \item Project Leader: 배유석 (Yuseok Bae)
	\end{innerlist}
\end{outerlist}
\vspace{0.5cm}

2023년 대한민국 재난안전 연구개발 행정안전부 장관상 (National Disaster Management R\&D Award, Ministry of the Interior and Safety, South Korea), 참여연구원 \hfill \textbf{2023}
\begin{outerlist}
\item[] \textit{영상 이해 인공지능 핵심기술을 통한 공공 CCTV 활용 시민 안전 실증 및 사업화}%
    \begin{innerlist}
	    \item Project Leader: 배유석 (Yuseok Bae)
	\end{innerlist}
\end{outerlist}
\vspace{0.5cm}

ETRI 우수연구실적상, ETRI 저널 논문 부문  \hfill \textbf{2022}
\vspace{0.5cm}

2021년 국가연구개발 우수성과 100선  (National R\&D Excellence Top 100, Minister of Science and ICT, South Korea), 참여연구원 \hfill \textbf{2021}
\begin{outerlist}
\item[] \textit{사람의 행동을 정밀하게 이해하는 시각지능 핵심 원천 기술 확보 및 실세계 적용 응용 기술 개발}%
    \begin{innerlist}
	    \item Project Leader: 배유석 (Yuseok Bae)
	\end{innerlist}
\end{outerlist}
\vspace{0.5cm}

Best Paper Award, ETRI Journal, \hfill \textbf{2020}
\begin{outerlist}
\item[] \textit{Vision-based Garbage Dumping Action Detection for Real-World Surveillance Platform}%
 \begin{innerlist}
	    \item 주저자 (1저자)
	\end{innerlist}
\end{outerlist}
\vspace{0.5cm}
		

ETRI 대표성과 (Representative Research) - 대상(Grand Prize), 참여연구원  \hfill \textbf{2020}
\begin{outerlist}
\item[] \textit{영상 내용을 사람처럼 이해하는 시각지능 원천 기술}%
    \begin{innerlist}
	    \item Project Leader: 박종열 (Jongyoul Park)
	\end{innerlist}
\end{outerlist}
\vspace{0.5cm}
		
2019년 국가연구개발 우수성과 100선  (National R\&D Excellence Top 100, Minister of Science and ICT, South Korea), 참여연구원 \hfill \textbf{2019}
\begin{outerlist}
\item[] \textit{대규모 시각 데이터 실시간 분석 및 내용 이해를 위한 디스커버리 플랫폼 (DeepView:딥뷰) 개발}%
    \begin{innerlist}
	    \item Project Leader: 박종열 (Jongyoul Park)
	\end{innerlist}
\end{outerlist}
\vspace{0.5cm}

ETRI 신입직원상 (New Employee Award), \hfill \textbf{2019}
\vspace{0.5cm}

Best Paper Award, CVPR workshop, \hfill \textbf{2013}
\begin{outerlist}
\item[] \textit{Detection of Moving Objects with Non-Stationary Cameras in 5.8ms:Bringing Motion Detection to your Mobile Device}%
    \begin{innerlist}
	    \item Workshop on Mobile vision in conjunction with CVPR
	    \item 공동저자 (2저자)
	\end{innerlist}
\end{outerlist}
\vspace{0.5cm}

송원김영환장학재단 장학생 (Songwon KimYoungHwan Scholarship), \hfill \textbf{2006--2013}
\vspace{0.5cm}
		
	
서울대학교 전기공학부 장학생, \hfill \textbf{2006}
% \end{bibsection}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{International School}
% International Computer Vision Summer School (\textbf{ICVSS}) $-$ Registration, Recognition and Reconstruction in Images and Video, 11-16 July 2011, Sampieri-Sicily, Italy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{교육 경력 (Teaching Experience)}
{ETRI AI Academy}, Daejeon, Korea
\begin{outerlist}
\item[] \textit{전문교수 (Professor) }%
		\begin{innerlist}
				\item Human Pose and its Application \hfill \textbf{2020, 2021, 2022}
				\item 범용 시각지능 모델의 이해 및 활용 실습 \hfill \textbf{2025 to Now}
		\end{innerlist}
\end{outerlist}
\vspace{0.5cm}

\href{http://www.dankook.ac.kr/en/web/international}{Dankook University},
Yongin, Korea
\begin{outerlist}
\item[] \textit{Guest Lecturer (6 week)}%
		\begin{innerlist}
				\item Machine Vision \hfill \textbf{April. 2016 to June. 2016}
		\end{innerlist}

\end{outerlist}
\vspace{0.5cm}
\href{http://www.useoul.edu/}{Seoul National University},
Seoul, Korea
\begin{outerlist}
\item[] \textit{Teaching Assistant}%

		\begin{innerlist}
				\item Convex Optimization
                                                    \hfill \textbf{Sep. 2012 to Dec. 2012}

				\item Introduction to Random Variables and Random Processes
				\hfill \textbf{Mar. 2012 to Jun. 2012}

		\end{innerlist}

\end{outerlist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Position of Responsibilities}
% Student Leader of Perception and Intelligence Lab, SNU (from Nov. 2013 to Oct. 2014)
% \begin{innerlist}
% 	\item Was in charge of project scheduling, job distributing, and coordinating feedback of research members.
% \end{innerlist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{연구 프로젝트 (Research Project Experience)}

\textit{Development of Artificial Intelligence Technology for Self-Improving Competency-Aware Learning Capabilities}%
				\hfill \textbf{Mar. 2024 to now}
\begin{innerlist}
\item This work was supported by Institute of Information \& Communications Technology Planning \& Evaluation (IITP) grant funded by the Korea government (MSIT).
\end{innerlist}
\blankline


\textit{Development of High Performance Visual BigData Discovery Platform for Large-Scale Realtime Data Analysis}%
				\hfill \textbf{Feb. 2017 to Feb. 2024}
\begin{innerlist}
\item This work was supported by Institute of Information \& Communications Technology Planning \& Evaluation (IITP) grant funded by the Korea government (MSIT).

\end{innerlist}
\blankline

\textit{Development of Previsional Intelligence based on Long-term Visual Memory Network}%

				\hfill \textbf{Jan. 2020 to Feb. 2022}
\begin{innerlist}
\item This work was supported by Institute of Information \& Communications Technology Planning \& Evaluation (IITP) grant funded by the Korea government (MSIT).

\end{innerlist}
\blankline




\textit{Deep Learning based Object detection and Recognition}%
				\hfill \textbf{Apr. 2015 to Feb. 2016}
\begin{innerlist}
\item Sponsored by the SAIT Samsung Electronics. The goal of the project is developing detection and recognition algorithms in a driver's view. 

\end{innerlist}

\blankline

\textit{Development of Predictive Visual Intelligence Technology}%
				\hfill \textbf{Apr. 2014 to Feb. 2016}
\begin{innerlist}
\item Sponsored by the ICT R\&D program of MSIP/IITP. The goal of the project is developing predicting algorithms such as traffic flows.

\end{innerlist}

\blankline

\textit{UAV Visual Surveillance System}%
                \hfill \textbf{Apr. 2013 to Feb. 2015}
\begin{innerlist}
\item Sponsored by Samsung S1. The goal of the project is developing visual surveillance algorithms for unmanned aerial videos such as moving object detection in a non-stationary camera.
\end{innerlist}

\blankline

\textit{Intelligent Visual Surveillance System}%
				\hfill \textbf{Mar. 2010 to Aug. 2013}


\begin{innerlist}
\item Sponsored by Samsung Techwin Co., Ltd. The goal of the project is developing visual analysis algorithms, such as background subtraction, object tracking and behavior understanding, and integrated system.
%
%Especially I developed a speed boosting method for background subtraction, which speeded up computational time by four times without performance degradation. Our resesarch group and I developed an intelligent visual surveillance named as \textit{PIL-EYE system}. The system architecture is extensible and flexible that it improves algorithm developing time and algorithm performance.  Also I served as a project leader in charge of a project scheduling and job distributing. I coordinated feedback of research members and Samsung Techwin company.

\end{innerlist}

\section{학술지/학회 리뷰 (Reviewers)}
CVPR, ICCV, WACV, BMVC

(Outstanding reviewer awards at CVPR'25)

IEEE Transactions on Neural Networks and Learning Systems

IEEE Transactions on Image Processing

IEEE Transactions on Vehicular Technology

IEEE Transactions on Multimedia

IEEE Transactions on Intelligent Transportation Systems.

IEEE Access





\section{최종 갱신일 (Last updated)} 
November 3, 2025



\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%% End CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%